---
title: "Political and Environmentalist Self-Identification"
author: "Anastasia Kunz"
date: "12/1/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(here)
library(tidyverse)
library(janitor)
library(broom)
library(kableExtra)
```

## Introduction 

In this report I will describe the association between respondents’ political affiliation (conservative or liberal) and if they consider themselves an environmentalist. To do this, I will compare the proportions of individuals who declare themselves environmentalists, non-environmentalists or unsure of both the liberal and conservative political identification. I will use a chi-squared test to asses whether there is a significant association between these two variables. 

```{r}
# read in data
survey_data <- read_csv(here("data", "conservation_survey.csv"))
```

```{r}
# Make subset of data for only what is needed in the task
survey_subset <- survey_data %>% 
  select(ENV_ID, POL_OR)
```

```{r}
# Add column to bin political party
party_subset_na <- survey_subset %>% 
  mutate(pol_party = case_when(
    POL_OR %in% c(1,2,3) ~ "Conservative", 
    POL_OR %in% c(5,6,7) ~ "Liberal"
  ))
party_subset <-na.omit(party_subset_na)
```

```{r}
#Add column to bin response
response_party <- party_subset %>% 
  mutate(response = case_when(
    ENV_ID == 1 ~ "Yes",
    ENV_ID == 2 ~ "No",
    ENV_ID == 3 ~ "Unsure"
  ))
```

**Table 1.** Self identification survey of political party and environmentalist. Data: Forest & Batavia 2017
```{r}
# Create finalized display table 
response_count <- response_party %>% 
  tabyl(pol_party, response) %>% 
  adorn_percentages() %>% 
  adorn_pct_formatting() %>% 
  adorn_ns()


response_count %>% 
  kable(col.names = c(" ",
                      "No",
                      "Unsure",
                      "Yes")) %>% 
  column_spec(1, bold = TRUE) %>% 
  kable_styling(full_width = FALSE)


```
 

```{r}
#create contingency table in correct format (no column names)
response_survey <- response_party %>% 
  tabyl(pol_party, response)

response_contingency <- response_survey %>% 
  column_to_rownames(var = "pol_party")


```




```{r include = FALSE}

#Run Chi Squared Test 
response_x2 <- chisq.test(response_contingency)

response_tidy <- tidy(response_x2)
response_tidy


```

Using a chi-squared statistical test, we find that there is a significant association between self declared political party and an individual's environmentalist response ($\chi$^2^(`r response_tidy$parameter`) = `r round(response_tidy$statistic,2)`, *p* = `r format(response_tidy$p.value, scientific = TRUE, digits = 3)`). Looking at the proportions in Table 1, we see that around 50% of conservatives declare themselves as *not* environmentalists, while only around 34% do. There is a small proportion (16%) that are unsure. However, when looking at liberal responses, we see this trend is flipped. Around 54% of liberals declare themselves environmentalists, with only 24% not environmentalists, and again, a small proportion is unsure (21%). Based on this sample and analysis, we see that these two variables are not independent of each other; political party is associated with whether individuals consider themselves environmentalists. 


## References 

Andrews Forest LTER Site and C. Batavia. 2019. Influences on charitable giving for conservation: Online survey data of 1,331 respondents across the US, August 2017 ver 3. Environmental Data Initiative. https://doi.org/10.6073/pasta/926e6270e324a1322a900da14d38b96c

