---
title: "Assignment 6 Task 3 CHANGE TITLE"
author: "Anastasia Kunz"
date: "12/1/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(here)
library(tidyverse)
library(janitor)
library(kableExtra)
```

```{r}
#read in data
lizards <- read_csv(here("data", "lizards (1).csv"))
```

## Introduction

2 - 3 sentence mini-introduction describing the data, the question you’re answering, and the method you’ll use

```{r}
#create a subset with desired variables, filtered for females of the two species
lizard_subset_na <- lizards %>% 
  select(total_length, sex, spp) %>% 
  filter(sex == "F") %>% 
  filter(spp %in% c("CNUN", "CNTE"))
lizard_subset <- na.omit(lizard_subset_na)
```

```{r}
# Create visualization comparing tail length between species
ggplot(lizard_subset, aes( x = spp, y = total_length))+
  geom_boxplot()
```

**Figure 1.** Caption here. Data: 

**Table 1.** Caption here. Data:
```{r}
# Create Summary Table
lizard_summary <- lizard_subset %>% 
  group_by(spp) %>% 
  summarize(mean_tail = mean(total_length),
            sdev_tail = sd(total_length),
            n = n())

```

```{r include = FALSE}
# exploratory plots


```

```{r}
#ttest here? come back to this
```


```{r}
# Determine cohen's d effect size
```


1 - 2 sentence summary statement describing your findings, that at least includes: the results of your hypothesis test, the effect size, and the actual means difference between the two group


## References

Lightfoot, D. 2017. Lizard pitfall trap data (LTER-II, LTER-III) ver 36. Environmental Data Initiative. https://doi.org/10.6073/pasta/ff37b4cace16a9943575f3fd7067064e 



