---
title: "Lizard Tail Length Comparison"
author: "Anastasia Kunz"
date: "12/1/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(here)
library(tidyverse)
library(janitor)
library(kableExtra)
library(effsize)
library(broom)
```

```{r}
#read in data
lizards <- read_csv(here("data", "lizards (1).csv"))
```

## Introduction

In this report, I will be using the Jornada Basin LTER lizards data to visualize and assess if there is a difference between tail lengths of female Colorado Checkered Lizards and female Desert Grassland Lizards. To do this I will perform statistical analysis using a two sample t-test comparing the mean total tail length for both groups, and calculate effect size. 

```{r}
#create a subset with desired variables, filtered for females of the two species
lizard_subset_na <- lizards %>% 
  select(total_length, sex, spp) %>% 
  filter(sex == "F") %>% 
  filter(spp %in% c("CNUN", "CNTE"))
lizard_subset <- na.omit(lizard_subset_na)
```

```{r}
# Create visualization comparing tail length between species
ggplot(lizard_subset, aes( x = spp, y = total_length))+
  geom_boxplot(aes(fill= spp))+
  theme_bw()+
  labs(
    x = "Species",
    y = "Tail Length (mm)",
    title = "Tail Length Comparison Between Two Species of Female Lizards",
    subtitle = "Lightfoot 2017"
  )+
   scale_x_discrete(labels=c("CNTE" = "Colorado Checkered Lizard", "CNUN" = "Desert Grassland Lizard"))+
  theme(legend.position = "none")
```

**Figure 1.** Box plot depicting total tail length comparison of female lizards between the Colorado Checkered Lizard and the Desert Grassland Lizard. Data: Lightfoot 2017

**Table 1.** Summary table of comparing tail length of female Colorado Checkered Liard and female Desert Grassland Lizard. Data: Lightfoot 2017
```{r}
# Create Summary Table
lizard_summary <- lizard_subset %>% 
  group_by(spp) %>% 
  summarize(mean_tail = mean(total_length),
            sdev_tail = sd(total_length),
            n = n())
lizard_summary %>% 
  kable(col.names = c("Species",
                      "Mean Tail Length (mm)",     # CHECK THE UNITS
                      "Standard Deviation (mm)",
                      "Sample Size (n)")) %>% 
  kable_styling(full_width = FALSE)
```


```{r include = FALSE}
# Create subsets

CNUN_tail <- lizard_subset %>% 
  filter(spp == "CNUN") %>% 
  pull(total_length)

CNTE_tail <- lizard_subset %>% 
  filter(spp == "CNTE") %>% 
  pull(total_length)

# exploratory plots
hist(CNUN_tail) # looks decently normal, slight skew to the right
hist(CNTE_tail) # looks pretty normal too, again slightly shifted right
qqnorm(CNUN_tail) # a little curved but mostly linear
qqnorm(CNTE_tail) # a little less normal, generally linear but doesnt look great

```

```{r}
#Run a two sample t test to compare means of two lizard species
tail_test<- t.test(CNUN_tail, CNTE_tail)
tail_test_tidy <- tidy(tail_test)

```


```{r}
# Determine cohen's d effect size
lizard_effsize <- cohen.d(CNTE_tail,CNUN_tail)

```

In this analysis I compared mean total tail length (mm) of female Colorado Checkered Lizards with female Desert Grassland Lizards, finding that the Colorado Checkered Lizard had a longer mean tail length (`r round(lizard_summary[1,2], 2)`mm, n = `r lizard_summary[1,4]`) than the Desert Grassland Lizard (`r round(lizard_summary[2,2], 2)`mm, n = `r lizard_summary[2,4]`) with an actual difference in means of `r round(lizard_summary[1,2]- lizard_summary[2,2], 2)`mm. This shows a a `r round((lizard_summary[1,2] - lizard_summary[2,2])/((lizard_summary[2,2] + lizard_summary[1,2])/2)*100, 2)`% difference (Table 1). Statistical anlaysis using a two-sample t-test showed this difference to be significant (Welch's Two Sample T Test: `r round(tail_test_tidy[1,4], 2)`, p< `r round(tail_test_tidy[1,5], 2)`), but with a small effect size (Cohen's d = `r round(lizard_effsize$estimate, 2)`))


## References

Lightfoot, D. 2017. Lizard pitfall trap data (LTER-II, LTER-III) ver 36. Environmental Data Initiative. https://doi.org/10.6073/pasta/ff37b4cace16a9943575f3fd7067064e 



