---
title: "Assignment 6 Task 2 CHANGE TITLE"
author: "Anastasia Kunz"
date: "12/1/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(here)
library(tidyverse)
library(janitor)
library(broom)
library(kableExtra)
```

## Introduction 

 a 2 - 3 sentence mini-introduction describing the survey data, the question you’re answering, and the method you’ll use

```{r}
# read in data
survey_data <- read_csv(here("data", "conservation_survey.csv"))
```

```{r}
# Make subset of data for only what is needed in the task
survey_subset <- survey_data %>% 
  select(ENV_ID, POL_OR)
```

```{r}
# Add column to bin political party
party_subset_na <- survey_subset %>% 
  mutate(pol_party = case_when(
    POL_OR %in% c(1,2,3) ~ "Conservative", 
    POL_OR %in% c(5,6,7) ~ "Liberal"
  ))
party_subset <-na.omit(party_subset_na)
```

```{r}
#Add column to bin response
response_party <- party_subset %>% 
  mutate(response = case_when(
    ENV_ID == 1 ~ "Yes",
    ENV_ID == 2 ~ "No",
    ENV_ID == 3 ~ "Unsure"
  ))
```

```{r}
# Create table 
response_count <- response_party %>% 
  tabyl(pol_party, response)
```
 
**Table 1.** Self identification survey of political party and environmentalist. Data: Forest & Batavia 2017
```{r = include}
#create contingency table 
response_table <- response_count %>% 
  column_to_rownames(var = "pol_party")

response_table %>% 
  kable(col.names = c("No",
                      "Unsure",
                      "Yes")) %>% 
  kable_styling(full_width = FALSE)

```
**Table 2.** Chi-Squared test results measuring impact FIX ME. Data: Forest & Batavia 2017.
```{r}

response_x2 <- chisq.test(response_table)

response_tidy <- tidy(response_x2)

response_tidy %>% 
  kable(col.names = c("Statistic",
                      "P-Value",
                      "Parameter",
                      "Method")) %>% 
  kable_styling(full_width = FALSE)

# ASK IN OFFICE HOURS WHY IT ROUNDS PVAL TO 0 AND IF THERE IS A WAY TO CHANGE IT? Necessary?
```

2-3 sentences, using in-line referencing to the chi-square test results, describe the results of the statistical test and briefly highlight major takeaways that your reader should learn from your analysis (i.e., you should refer to the actual proportions here).

## References 

Andrews Forest LTER Site and C. Batavia. 2019. Influences on charitable giving for conservation: Online survey data of 1,331 respondents across the US, August 2017 ver 3. Environmental Data Initiative. https://doi.org/10.6073/pasta/926e6270e324a1322a900da14d38b96c

